A comparison of classification algorithms applied to the Adult Database

### 2009-12-09 report/final.tex
added preliminary CN2 experimental context description.

@@

>>>>

\subsection{CN2}

CN2 \cite{cn2} is a learning algorithm for rule induction \cite{rule_induction}
that isn't available in Weka nor in RapidMiner. CN2 inductively learns a set of
propositional if...then.. rules from a set of training examples, performing a
general-to-specific beam search through the rule space for the "best" rule, 
removing training examples covered by it, and repeating it until no more "good"
rules can be found. The original version of the algorithm used entropy and
significance test to decide the best rule. Later, it was improved to use the
Laplace estimate \cite{cn2_laplace}, which is implemented in Peter Clark's 
software used for our testing purposes.

Peter Clark's CN2 software is built in C and provides a command-line environment
for conducting experiments. The input format is limited to two files, one
defining the attributes and other defining the training examples. The software 
also provides an environment for performance evaluation of the produced set of 
rules, by accepting a test file with examples.

Only the following values are feed into the algorithms: age, workclass, 
education, marital\_status, occupation, relationship, race, sex, capital\_gain,
capital\_loss, hours\_per\_week, native\_country, and plus\_50. The attributes
education\_num and fnlwgt are derived from other attributes and so are kept out.
In terms of data pre-processing for missing values, continuous values were 
replaced by the average value, while discrete values were replaced by the mode.

In terms of performance metris, we took into account the error rate and the time
spent building the rule set.

@@

\bibitem{cn2_laplace}
Peter Clark and Robin Boswell. Rule induction with CN2: Some recent improvements. In Y. Kodratoff, editor, Machine Learning - EWSL-91, pages 151-163, Berlin, 1991. Springer-Verlag.
